The Evolution of Phenotypically Invariant Genetic Networks

### 2017-12-08 kalman_walk_paper.tex
a few more bibtex fixes

We will suppose that each organism's phenotype is determined by its vector of coefficients, denoted by $x=(x_1, x_2, \ldots, x_p)$,
and that the corresponding fitness is determined by the distance of its phenotype to optimum.
The optimum phenotype is unique, but is realized by many distinct $x$ -- those falling in the ``optimal set'' $\allS$.
The phenotypic distance to optimum of an organism with coefficients $x$ is denoted $D(x)$.
In the results above, $x = (A,B,C)$ and $D(x)$ is given by equation \eqref{eqn:distance}.
The fitness of an organism with coefficients $x$ will be $\exp(-D(x)^2)$.
% this assumption does not entail a loss of generality since $D$ is arbitrary.
We assume that in the region of interest, the map $D$ is smooth
and that we can locally approximate the optimal set $\allS$ as a quadratic surface.
As above, an individual's coefficients are given by averaging its parentally inherited coefficients and adding random noise due to segregation and possibly new mutation.
Concretely, we use the \emph{infinitesimal model} for reproduction \citep{barton2016infinitesimal} --
the offspring of parents at $x$ and $x'$ will have coefficients $(x+x')/2 + \varepsilon$,
where $\varepsilon$ is a random Gaussian displacement due to random assortment of parental alleles.

>>>>

We will suppose that each organism's phenotype is determined by its vector of coefficients, denoted by $x=(x_1, x_2, \ldots, x_p)$,
and that the corresponding fitness is determined by the distance of its phenotype to optimum.
The optimum phenotype is unique, but is realized by many distinct $x$ -- those falling in the ``optimal set'' $\allS$.
The phenotypic distance to optimum of an organism with coefficients $x$ is denoted $D(x)$.
In the results above, $x = (A,B,C)$ and $D(x)$ is given by equation \eqref{eqn:distance}.
The fitness of an organism with coefficients $x$ will be $\exp(-D(x)^2)$.
% this assumption does not entail a loss of generality since $D$ is arbitrary.
We assume that in the region of interest, the map $D$ is smooth
and that we can locally approximate the optimal set $\allS$ as a quadratic surface.
As above, an individual's coefficients are given by averaging its parentally inherited coefficients and adding random noise due to segregation and possibly new mutation.
Concretely, we use the \emph{infinitesimal model} for reproduction \citep{barton2017infinitesimal} --
the offspring of parents at $x$ and $x'$ will have coefficients $(x+x')/2 + \varepsilon$,
where $\varepsilon$ is a random Gaussian displacement due to random assortment of parental alleles.
